Stochastic Variance-Reduced Policy Gradient

### 2018-02-08 svrpg.tex
Updated

\Ets{\norm[]{\vtheta_{t+1}^{s+1}-\wt{\vtheta}^s}^2} 
&= \Ets{\norm[]{\vtheta_{t+1}^{s+1}- \vtheta_t^{s+1} + \vtheta_t^{s+1}-\wt{\vtheta}^s}^2} \nonumber\\

@@

+2\alpha_t\Ets{\frac{1}{2\beta}\norm[]{\gradJ{\vtheta_t^{s+1}}}^2+\frac{\beta}{2}\norm[]{\vtheta_t^{s+1}-\wt{\vtheta}^s}^2} \label{eq:16a}\\ 

@@

Finally:

@@

	R_{t+1}^{s+1} &= \Ets{J(\vtheta_{t+1}^{s+1}) - c_{t+1}\norm[]{\vtheta_{t+1}^{s+1}-\tilde{\vtheta}^s}^2} \nonumber\\

@@

	&\geq	\Ets{J(\vtheta_t^{s+1})+\frac{\alpha_t}{2}\norm[]{\gradJ{\vtheta_t^{s+1}}}^2 - \frac{\alpha_t^2L}{2}\norm[]{\gradBlack{\vtheta_t^{s+1}}}^2} \nonumber\\

@@

	&\qquad-2c_{t+1}\alpha_t\Ets{\frac{1}{2\beta}\norm[]{\gradJ{\vtheta_t^{s+1}}}^2+\frac{\beta}{2}\norm[]{\vtheta_t^{s+1}-\tilde{\vtheta}^s}^2} \nonumber\\ 

@@

	+\frac{\alpha_t}{2}\left(1-\frac{2c_{t+1}}{\beta}\right)\Ets{\norm[]{\gradJ{\vtheta_t^{s+1}}}^2} \nonumber\\

@@

	&\geq  \Ets{J(\vtheta_t^{s+1})} - c_{t+1}\left(1+\alpha_t\beta+\alpha_t\right)\Ets{\norm[]{\vtheta_{t}^{s+1}-\tilde{\vtheta}}^2} \nonumber\\

@@

	+\frac{\alpha_t}{2}\left(1-2\frac{c_{t+1}}{\beta}\right)\Ets{\norm[]{\gradJ{\vtheta_t^{s+1}}}^2} \nonumber\\

@@

	& = \Ets{J(\vtheta_t^{s+1}) - \left(c_{t+1}\left(1+\alpha_t\beta+\alpha_t+\frac{\alpha_t^2L^2}{B}\right)+\frac{\alpha_t^2L^3}{2B}\right)\norm[]{\vtheta_{t}^{s+1}-\tilde{\vtheta}}^2} \nonumber\\

@@

	+\alpha_t\left(\frac{1}{2}-\frac{c_{t+1}}{\beta}-\frac{\alpha_tL}{2}-\alpha_tc_{t+1}\right)\Ets{\norm[]{\gradJ{\vtheta_t^{s+1}}}^2} \nonumber\\

@@

where (\ref{eq:17}) is from (\ref{eq:13}), (\ref{eq:18}) is from (\ref{eq:16}), (\ref{eq:19}) is from Lemma \ref{lemma:aux2}, and (\ref{eq:20}) is from Assumption \ref{ass:REINFORCE}.

>>>>

        \mathbb{E}_{t|s}\bigg[ & \norm[]{\vtheta_{t+1}^{s+1}-\wt{\vtheta}^s}^2 \bigg]
= \Ets{\norm[]{\vtheta_{t+1}^{s+1}- \vtheta_t^{s+1} + \vtheta_t^{s+1}-\wt{\vtheta}^s}^2} \nonumber\\

@@

+2\alpha_t\Ets{\frac{1}{2\beta_t}\norm[]{\gradJ{\vtheta_t^{s+1}}}^2+\frac{\beta_t}{2}\norm[]{\vtheta_t^{s+1}-\wt{\vtheta}^s}^2} \label{eq:16a}\\ 

@@

Let's us consider the following function:
	R_{t+1}^{s+1} \coloneqq \Ets{J(\vtheta_{t+1}^{s+1}) - c_{t+1}\norm[]{\vtheta_{t+1}^{s+1}-\tilde{\vtheta}^s}^2}. 
The objective is now to provide a lower bound to it.

@@

	R_{t+1}^{s+1} 
    % &= \Ets{J(\vtheta_{t+1}^{s+1}) - c_{t+1}\norm[]{\vtheta_{t+1}^{s+1}-\tilde{\vtheta}^s}^2} \nonumber\\

@@

	%&\geq	\Ets{J(\vtheta_t^{s+1})+\frac{\alpha_t}{2}\norm[]{\gradJ{\vtheta_t^{s+1}}}^2 - \frac{\alpha_t^2L}{2}\norm[]{\gradBlack{\vtheta_t^{s+1}}}^2} \nonumber\\
	&\geq	\Ets{J(\vtheta_t^{s+1}) - \frac{\alpha_t^2L}{2}\norm[]{\gradBlack{\vtheta_t^{s+1}}}^2}
    + \EVV[t-1|s]{\frac{\alpha_t}{2}\norm[]{\gradJ{\vtheta_t^{s+1}}}^2}

@@

	&\qquad-2c_{t+1}\alpha_t\Ets{\frac{1}{2\beta_t}\norm[]{\gradJ{\vtheta_t^{s+1}}}^2+\frac{\beta_t}{2}\norm[]{\vtheta_t^{s+1}-\tilde{\vtheta}^s}^2} \nonumber\\ 

@@

	+\frac{\alpha_t}{2}\left(1-\frac{2c_{t+1}}{\beta_t}\right)\Ets{\norm[]{\gradJ{\vtheta_t^{s+1}}}^2} \nonumber\\

@@

	&\geq  \Ets{J(\vtheta_t^{s+1})} - c_{t+1}\left(1+\alpha_t\beta_t+\alpha_t\right)\Ets{\norm[]{\vtheta_{t}^{s+1}-\tilde{\vtheta}}^2} \nonumber\\

@@

	+\frac{\alpha_t}{2}\left(1-2\frac{c_{t+1}}{\beta_t}\right)\Ets{\norm[]{\gradJ{\vtheta_t^{s+1}}}^2} \nonumber\\

@@

	& = \Ets{J(\vtheta_t^{s+1}) - \left(c_{t+1}\left(1+\alpha_t\beta_t+\alpha_t+\frac{\alpha_t^2L^2}{B}\right)+\frac{\alpha_t^2L^3}{2B}\right)\norm[]{\vtheta_{t}^{s+1}-\tilde{\vtheta}}^2} \nonumber\\

@@

	+\alpha_t\left(\frac{1}{2}-\frac{c_{t+1}}{\beta_t}-\frac{\alpha_tL}{2}-\alpha_tc_{t+1}\right)\Ets{\norm[]{\gradJ{\vtheta_t^{s+1}}}^2} \nonumber\\

@@

where~\eqref{eq:17} is from~\eqref{eq:13} noticing that $\EVV[t|s]{\norm[]{\nabla J(\vtheta^{s+1}_t)}^2} = \EVV[t|s]{\norm[]{\nabla J(\vtheta^{s+1}_t)}^2}$,~\eqref{eq:18} is from~\eqref{eq:16},~\eqref{eq:19} is from Lemma~\ref{lemma:aux2}, and (\ref{eq:20}) is from Assumption \ref{ass:REINFORCE}.
